---
title: "WKSHP1FINALEQMDCODE"
author: "Thrall H."
format: html
editor: visual
---
---
title: "WKSHP1 FINAL QMD CODE"

format:
  html:
    theme: cosmo
    highlight-style: a11y
    toc: true
    toc-depth: 3
    toc-location: left
    toc-title: "Contents"
    number-sections: true
    code-fold: true
    code-summary: "Show code"
    code-tools: true
    code-copy: true
    embed-resources: true
    df-print: paged
    fig-height: 5
    fig-width: 8
    fig-responsive: true
    smooth-scroll: true
---

# Load packages
```{r}
#| include: false
library(tidyverse)
```

# Load penguin dataset
```{r}
getwd()
penguins <- read_csv(here::here("data/penguins.csv"))
```
# Initial investigations
```{r}
head(penguins)
str(penguins)
```



```{r}
mass_compare_plot <- penguins |>
  group_by(species, island) |>
  summarise(
    mean_mass = mean(body_mass_g, na.rm = TRUE),
    sd_mass = sd(body_mass_g, na.rm = TRUE),
    n = n(),
    .groups = "drop"
  ) |>
  ggplot(aes(x = species, y = mean_mass, colour = island)) +
  geom_point(size = 3) +
  geom_errorbar(
    aes(
      ymin = mean_mass - sd_mass,
      ymax = mean_mass + sd_mass
    ),
    width = 0.2
  ) +
  labs(
    title = "Mean Body Mass by Species and Island",
    subtitle = "Error bars represent standard deviation",
    y = "Mean Body Mass (g)",
    x = "Species"
  ) +
  theme_minimal()

mass_compare_plot
```

```{r}
mass_compare_plot <- penguins |>
  group_by(species, island) |>
  summarise(
    mean_mass = mean(body_mass_g, na.rm = TRUE),
    sd_mass = sd(body_mass_g, na.rm = TRUE),
    n = sum(!is.na(body_mass_g)),
    se_mass = sd_mass / sqrt(n),
    .groups = "drop"
  ) |>
  ggplot(aes(x = species, y = mean_mass, colour = island)) +
  geom_point(size = 3) +
  geom_errorbar(
    aes(
      ymin = mean_mass - se_mass,
      ymax = mean_mass + se_mass
    ),
    width = 0.2
  ) +
  labs(
    title = "Mean Body Mass by Species and Island",
    subtitle = "Error bars represent standard error",
    x = "Species",
    y = "Mean Body Mass (g)",
    colour = "Island"
  ) +
  theme_minimal()

mass_compare_plot
```

```{r}
mass_summary <- penguins |>
  group_by(species, island) |>
  summarise(
    mean_mass = mean(body_mass_g, na.rm = TRUE),
    sd_mass = sd(body_mass_g, na.rm = TRUE),
    n = sum(!is.na(body_mass_g)),
    se_mass = sd_mass / sqrt(n),
    .groups = "drop"
  )

mass_summary
```

```{r}

```
